---
title: "Lab 8 Notes"
author: "German Silva"
date: "11/15/2021"
output: html_document
---

**Lab 8 Objectives:**

- Explore multivariate data (SLO housing prices)
- Perform multiple linear regression
- Assess diagnostics
- Compare different models by AIC
- Explain model outputs
- Make a nice table of regression results
- Make predictions using a final model
- git branch

```{r setup, include = TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Attach packages

library(tidyverse)
library(here)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
library(janitor)
```

- Read in data being used in the lab
- Make a subset called homes_sub that only contains observations from the following cities:
  - San Luis Obispo
  - Arroyo Grande
  - Atascadero
  - Santa Maria-Orcutt

```{r}
homes <- read_csv(here("data", "slo_homes.csv"))

homes_sub <- homes %>% 
  clean_names() %>% 
  filter(city %in% c("Arroyo Grande", "San Luis Obispo", "Atascadero", "Santa Maria-Orcutt"))

```

# Do a little exploring of the data


Summary statistics (home price, based on city and sale status):

- Find and return in a nice summary table the mean and standard deviation of home price, grouped by city and sale status

```{r, include = FALSE, eval=FALSE}
homes_sub_stats <- homes_sub %>% 
  group_by(city, status) %>% 
  summarize(mean_price = mean(price),
            sd_price= sd(price))

kableExtra::kable(homes_sub_stats)

# actually i don't even want to run this code: eval = FALSE

ggplot(homes_sub, aes(x=price)) +
  geom_density(aes(color= city, fill=city), alpha = 0.3) +
  scale_x_continuous(limits = c(0, 3e6))
```

Explore the relationship between square footage and home price. CHange color by city and shape by sales status

```{r}
ggplot(homes_sub, aes(x= sq_ft, y= price)) +
  geom_point(aes(color= city, shape = status)) +
  geom_smooth(method="lm")



```

## Model the relationship with home price as DV

```{r}
homes_lm1 <- lm(price ~ city + sq_ft + status + bedrooms + bathrooms + price_per_sq_ft, data = homes_sub) # price per sq ft is redundant, bedrooms and bathrooms may be correlatedd, sqft is also connected to those. 

# Make a subset that only contains the quantitative vairables

homes_quant <- homes_sub %>% 
  select(price, bedrooms, bathrooms, sq_ft, price_per_sq_ft)
homes_corr <- cor(homes_quant)
homes_corr

corrplot(homes_corr, method = "ellipse")

# How wold i explor diagnostic plots?

plot(homes_lm1)

```

Try another model where we simplify this a bit:
- City
- SqFt
- Status

```{r}
homes_lm2 <- lm(price ~ city + sq_ft + status, data = homes_sub)

plot(homes_lm2)
```

Find the AIC value of each model
```{r}
AIC(homes_lm1)
AIC(homes_lm2)
```

Try another permutation of this model that you think might make sense, check out and cpmpare the model fit, outputs, and AIC value

```{r}
homes_lm3 <- lm(price ~ sq_ft + city + status + bedrooms + bathrooms, data = homes_sub)

homes_lm4 <- lm(price ~ sq_ft + city + status + bathrooms, data = homes_sub)

homes_lm5 <- lm(price ~ sq_ft + city + status + bedrooms, data = homes_sub)

homes_lm6 <- lm(price ~ price_per_sq_ft + city + status, data = homes_sub)

homes_lm7 <- lm(price ~ sq_ft + city, data = homes_sub)
```

```{r}
AIC(homes_lm1)
AIC(homes_lm2)
AIC(homes_lm3)
AIC(homes_lm4)
AIC(homes_lm5)
AIC(homes_lm6)
AIC(homes_lm7)
```

Use `modelsummary` to show model outputs side-by-side:

If you use modelsummary to return model outputs of multiple models, it wants you to feedit to it as a list
```{r}

modelsummary(list(homes_lm1, homes_lm2, homes_lm5, homes_lm7))
```

## Start making predictions with this model

Use `broom::augment()`

```{r}
homes_predicted <- augment(homes_lm1)
```

Use the `predict()` function to try out your model on new scenarios that you create.


