---
title: "Lab 8 Notes"
author: "German Silva"
date: "11/15/2021"
output: html_document
---

**Lab 8 Objectives:**

- Explore multivariate data (SLO housing prices)
- Perform multiple linear regression
- Assess diagnostics
- Compare different models by AIC
- Explain model outputs
- Make a nice table of regression results
- Make predictions using a final model
- git branch

```{r setup, include = TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Attach packages

library(tidyverse)
library(here)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
library(janitor)
```

- Read in data being used in the lab
- Make a subset called homes_sub that only contains observations from the following cities:
  - San Luis Obispo
  - Arroyo Grande
  - Atascadero
  - Santa Maria-Orcutt

```{r}
homes <- read_csv(here("data", "slo_homes.csv"))

homes_sub <- homes %>% 
  clean_names() %>% 
  filter(city %in% c("Arroyo Grande", "San Luis Obispo", "Atascadero", "Santa Maria-Orcutt"))

```

# Do a little exploring of the data


Summary statistics (home price, based on city and sale status):

- Find and return in a nice summary table the mean and standard deviation of home price, grouped by city and sale status

```{r, include = FALSE, eval=FALSE}
homes_sub_stats <- homes_sub %>% 
  group_by(city, status) %>% 
  summarize(mean_price = mean(price),
            sd_price= sd(price))

kableExtra::kable(homes_sub_stats)

# actually i don't even want to run this code: eval = FALSE

ggplot(homes_sub, aes(x=price)) +
  geom_density(aes(color= city, fill=city), alpha = 0.3) +
  scale_x_continuous(limits = c(0, 3e6))
```

Explore the relationship between square footage and home price. CHange color by city and shape by sales status

```{r}
ggplot(homes_sub, aes(x= sq_ft, y= price)) +
  geom_point(aes(color= city, shape = status)) +
  geom_smooth(method="lm")

```

